### 2018-08-06 article.tex
tab width 2
Added Q-circuits example at beginning

\input{preamble.tex}
%%% some diagrams we won;t need in this papaer
%\input{tikzpreamble.tex}
%\input{quantumcircuits.tex}

@@

\begin{example}  \label{ex:quantum-circs}
  TODO -- quanutm circuits
\end{example}

>>>>

\input{preamble.tex}
\input{tikzpreamble.tex}
\input{quantumcircuits.tex}

@@

\begin{example}  \label{ex:quantum-circs}
  The main example of interest is \Circ, the PROP of quantum circuits.
  Different authors, and different hardware manufacturers, prefer
  different primitive gate sets but the following is typical:
  \[
  \begin{array}{cccccccccc}
    \circZ{{}} & \qquad  & \circX{{}} & \qquad & \circH \\ 
    \vstrut{1.2em}
    Z : 1 \to 1 && X : 1 \to 1 && H : 1 \to 1\\
    \\
    \circbox{R_Z(\theta)} & \qquad & \circCPhase{\theta} & \qquad & \circCX  \\ 
    \vstrut{1.2em}
    R_Z(\theta) : 1 \to 1 &&  \CPhase\theta :2 \to 2 && \CX : 2 \to 2\\
  \end{array}
  \]
  We omit the usual matrix interpretations but these can be found in
  the standard textbook \cite{NieChu:QuantComp:2000}.  Note that in
  this example we actually have an uncountable family of generating
  gates, one for each value $\theta \in [0,2\pi)$.  Unlike the case of
  Boolean circuits all quantum gates have the same number of inputs and
  outputs.  In fact, \Circ is a \dag-PROP, but this will not concern
  us here.
\end{example}
